---
title: "Part 1"
author: "Ruijie Ma"
date: "2018/3/17"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r setup???echo=TRUE}
library(tidyverse)
library(zoo)
library(TSA)
setwd("/Users/ruijie/Documents/ma415/Assignment5")
data <- NULL
time <- seq(1988,2017)
time <- time[-26]
n <- length(time)
for (i in 1:n){
  filename<-paste("46035h",time[i],".txt",sep = "")
  tex<-read.table(filename,header = TRUE, fill = TRUE)
  if(!is.null(data)){
    names(tex)<-names(data)
  }
  if(length(tex[1,])==16|length(tex[1,])==17){
    sub_tex<-tex[,c(1,2,3,4,13,14)]
  }
  if(length(tex[1,])==18){
    sub_tex<-tex[,c(1,2,3,4,14,15)]
  }
  names(sub_tex)<-c('YY','MM','DD','hh','ATMP','WTMP')
  data<-rbind(data,sub_tex)
}
data <- subset(data,data$ATMP!=999&data$WTMP!=999)
daily <- data %>%
group_by(MM,YY,DD)%>%
summarise(ATMP=mean(ATMP),WTMP=mean(WTMP))
daily[daily$YY<1999,]$YY<-daily[daily$YY<1999,]$YY+1900
daily$time<-paste(daily$YY,"-",daily$MM,"-",daily$DD,sep = "")
daily$time<-as.Date(daily$time,format = "%Y-%m-%d")
ATMP<- with(daily, zoo(ATMP, time))
WTMP<- with(daily, zoo(WTMP, time))

plot(ATMP,main = "daily Air Temperature" )
plot(WTMP,main = "Sea Air Temperature" )
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

