---
title: "HW 4"
author: "Ruijie Ma"
date: "2018/2/20"
output: pdf_document
---
##10.5
##1: The tibble does not have rownames and it adds the colnames automatically
##2: A data.frame does partial mathching which tibble doesn't. A data.frame returns a factor and the tibble returns a data frame.
##4:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tibble)
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
annoying$`1`
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ggplot(annoying,aes(x=`1`,y=`2`)) + geom_point()

annoying<-annoying %>% mutate(`3`=`2`/`1`)
annoying

annoying<-annoying%>%rename(one=`1`,two=`2`,three=`3`)
```
##5: enframe converts vectors and list to data.frame.It might be used when you are typing a list and want to use it as dataframe.
##12.6
##1:Yes, this is reasonable.There is a big difference between NA and 0 is that 0 will be counted as a vector.Therefore, it will changes the result of statistcal test.

##2:without doing so, the colname can not be saperated because of the format inconsistency.

##3:
```{r setup, include=F}
knitr::opts_chunk$set(echo = T)
tidyr::who
who1<-who %>% gather(new_sp_m014,newrel_f65,key="key",value="cases",na.rm=T)
who1
who2<-who1 %>% select(-iso2,-iso3)
who2
```

##4
```{r setup, include=F}
knitr::opts_chunk$set(echo = T)
gather(new_sp_m014:newrel_f65, na.rm = TRUE) %>% 
  mutate(code = stringr::str_replace(code, "newrel", "new_rel")) %>%
  separate(code, c("new", "var", "sexage")) %>% 
  select(-new, -iso2, -iso3) %>% 
  separate(sexage, c("sex", "age"), sep = 1)




