---
title: "MA415 Assign2 "
author: "Ruijie Ma"
date: "January 26, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.

(a) Write functions \texttt{tmpFn1} and \texttt{tmpFn2} such that if \texttt{xVec} is the vector $(x_1, x_2, ... ,x_n)$, then \texttt{tmpFn1(xVec)} returns vector $(x_1, x_2^2, ..., x_n^n)$ and \texttt{tmpFn2(xVec)} returns the vector $(x_1, \frac{x_2^2}{2}, ..., \frac{x_n^n}{n})$.

******

Here is \texttt{tmpFn1}
```{r}

tmpFn1 <- function(xVec){
  return(xVec^(1:length(xVec)))
}

## simple example
a <- c(2, 5, 3, 8, 2, 4)

b <- tmpFn1(a)
b

```

and now \texttt{tmpFn2}

```{r}
tmpFn2 <- function(xVec2){
  
  n = length(xVec2)
  
  return(xVec2^(1:n)/(1:n))
}



c <- tmpFn2(a)
c


```

######  
  
  
  
(b) Now write a fuction \texttt{tmpFn3} which takes 2 arguments $x$ and $n$ where $x$ is a single number and $n$ is a strictly positive integer.  The function should return the value of   
$$1 + \frac{x}{1} + \frac{x^2}{2} + \frac{x^3}{3} + ... + \frac{x^n}{n}$$
Here is \texttt {temfn3}
```{r} 
a<-c(2,3,4)
tmpFn3 <- function(x,n){
  n <- 1:length(x)
  return((sum((x^n)/n))+1)
}

b <- tmpFn3(a,n)

b



```
\newpage
### 2. Write a funciton \texttt{tmpFn(xVec)} such that if \texttt{xVec} is the vector $x = (x_1, ...,x_n)$ then \texttt{tmpFn(xVec)} returns the vector of moving averages:

$$\frac{x_1 + x_2 + x_3}{3}, \frac{x_2 + x_3 + x_4}{3}, ...,\frac{x_{n-2} + x_{n-1} + x_n}{3}$$

 \texttt{tmpFn}(c(1:5,6:1))
```{r}
temFn<-function(x)
  {
  n <- length(x)
  q <- x[1:(n-2)]
  w <- x[2:(n-1)]
  e <- x[3:n]
  return((q+w+e)/3)
}
b<- temFn(c(1:5,6:1))

b

```
### 3. Consider the continuous function

$$f(x) = \left\{\begin{matrix}
x^2 + 2x + 3 & if  & x < 0 \\ 
x + 3 & if & 0 \leq x < 2 \\ 
x^2 + 4x - 7 & if & 2 \leq  x 
\end{matrix}\right.$$

Write a function \texttt{tmpFn} which takes a single argument \texttt{xVec}.  the function should return the vector the values of the function $f(x)$ evaluated at the values in \texttt{xVec}.  
Hence plot the function $f(x)$ for $-3 < x <3$.

```{r}
temFn <- function(x){
 return(ifelse(x < 0, x^2 + 2*x + 3, ifelse(x < 2, x+3, x^2 + 4*x - 7)))
  }
q <- seq(-3,3)
p <- temFn(q)

plot(q,p)
```

### 4. Write a function which takes a single argument which is a matrix.  The function should return a matrix which is the same as the function argument but every odd number is doubled.  
Hence the result of using the function on the matrix   

$$\begin{bmatrix}
1 & 1 & 3\\ 
5 & 2 & 6\\ 
-2 & -1 & -3
\end{bmatrix}$$

should be:

$$\begin{bmatrix}
2 & 2 & 6\\ 
10 & 2 & 6\\ 
-2 & -2 & -6
\end{bmatrix}$$
```{r}
fun1 <- function(x){
  return(ifelse(x%%2==1,2*x,x))
  }
a <- matrix(1:9, nrow = 3, ncol = 3)
b <- fun1(a)

b
```

### 5. Write a function which takes 2 arguements $n$ and $k$ which are positive integers.  It should return the $\mathit{n} x \mathit{n}$ matrix:


$$\begin{bmatrix}
k & 1 & 0 & 0 & \cdots  & 0 & 0\\ 
1 & k & 1 & 0 & \cdots  & 0 & 0\\
0 & 1 & k & 1 & \cdots  & 0 & 0\\
0 & 0 & 1 & k & \cdots  & 0 & 0\\
\cdot & \cdot & \cdot & \cdot & \cdot & \cdot & \cdot\\ 
0 & 0 & 0 & 0 & \cdots  & k & 1\\
0 & 0 & 0 & 0 & \cdots  & 1 & k
\end{bmatrix}$$


```{r}
fun2 <- function(k,n){
  q<-diag(k,k,k)
  n<-abs(row(q)-col(q))
  mat<-q+n
return(ifelse(mat==k,k,ifelse(mat==1,1,0)))
  }
  b<-fun2(5,2)
  b
```
### 6. Suppose an angle $\alpha$ is given as a positive real number of degrees.  
If $0 \leq \alpha < 90$ then it is quadrant 1.  If $90 \leq \alpha < 180$ then it is quadrant 2.  
if $180 \leq \alpha < 270$ then it is quadrant3.  if $270 \leq \alpha < 360$ then it is quadrant 4.  
if $360 \leq \alpha < 450$ then it is quadrant 1.  
And so on ...   

Write a function \texttt{quadrant(alpha)} which returns the quadrant of the angle $\alpha$.

```{r}
fun4<-function(a){
  k<-a%%360
  return(ifelse(a<90,'quadrant1',ifelse(a<180,'quadrant2',ifelse(a<270,'quadrant3',ifelse(a<360,'quadrant4',0)))))
}
b<-fun4(269)
b
```
### 7.

(a) Zeller's congruence is the formula:

$$ f = ([2.6m - 0.2] + k + y + [y/4] + [c/4] - 2c)mod 7 $$
where $[x]$ denotes the integer part of $x$; for example $[7.5] = 7$.  

Zeller's congruence returns the day of the week $f$ given:

$k$ = the day of the month  
$y$ = the year in the century  
$c$ = the first 2 digits of the year (the century number)  
$m$ = the month number (where January is month 11 of the preceding year, February is month 12 of the preceding year, March is month 1, etc.)   
For example, the date 21/07/1`963 has $m = 5, k = 21, c = 19, y = 63$;  
the date 21/2/63 has $m=12, k=21, c=19, and y=62$.  
Write a function \texttt{weekday(day,month,year)} which returns the day of the week when given the numerical inputs of the day, month and year.  
Note that the value of 1 for $f$ denotes Sunday, 2 denotes Monday, etc.

(b) Does your function work if the input parameters \text{day, month, and year} are vectors with the same length and valid entries?

```{r}
weekday<-function(k,m,n){
  b<-m-2
  a<-c(ifelse(b==0,b+12&n-1,ifelse(b==-1,b+12&n-1,b)))
  g<-n%/%100
  p<-n%%100
  q<-floor(2.6*a-0.2)+k+p+floor(p/4)+floor(g/4)-2*g
  return(ifelse(q%%7==1,'Monday',ifelse(q%%7==2,'Tuesday',ifelse(q%%7==3,'Wednesday',ifelse(q%%7==4,'Thursday',ifelse(q%%7==5,'Friday',ifelse(q%%7==6,'Saturday',ifelse(q%%7==7,'Sunday','hi'))))))))
}
b<-weekday(3,2,2018)
b
```








